---
title: "Trial"
format: html
editor: visual
---

## Quarto

Reading data

```{r}
library(tidyverse)
library(lubridate)
#install.packages("tidytuesdayR")
```

```{r}



# Get the Data

brewing_materials <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewing_materials.csv')

beer_taxed <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_taxed.csv')
brewer_size <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewer_size.csv')
beer_states <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_states.csv')

# Or read in with tidytuesdayR package (https://github.com/thebioengineer/tidytuesdayR)
# PLEASE NOTE TO USE 2020 DATA YOU NEED TO USE tidytuesdayR version ? from GitHub

# Either ISO-8601 date or year/week works!

# Install via devtools::install_github("thebioengineer/tidytuesdayR")

tuesdata <- tidytuesdayR::tt_load('2020-03-31')
tuesdata <- tidytuesdayR::tt_load(2020, week = 14)


brewing_materials <- tuesdata$brewing_materials

brewing_materials <- brewing_materials %>%
  mutate(date=ymd(paste(year,month,1))) %>%
  filter(year<2016)
  
  
```

\- Types of ingredients and quantities used in beer production over time

. Using the brewing materials dataset, I will make a barplot (geom_col) for type and month_current variables, and fill using material_type. I will filter out anything that says total to exclude the totals and only keep individual values.

-   Relationship between total barrels produced and brewery size .Since brewery size is not a definite number, I can't do correlation analysis, I will just do visualize the data as is. .

From the brewer size dataset, I will create a graph showing the barrel number and brew size . Potentially look at where the beer is produced (might require a map)

-   Number of barrels consumed on premises vs barrels that end up in bottles&cans over time . Group by states and year . Calculate the percentage of barrels consumed (barrels/sum(barrels)) . filter those consumed only on premises and then in botles/cans . make a map that sorts colors based on percentages

-   

Number of barrels that are tax free and exported (Actually I can look at percent change since I have values for current and prior year) . Filter out barrels that are tax free (from tax status column) and for export(in type column) . Calculate the percent change ((current year value-prior year value)/prior year value)\*100 .Create a graph that shows change over the years

```{r}
#Question1
head(brewing_materials)

brewing_materials%>% 
  filter(!str_detect(material_type,"Total")) %>% 
  mutate(type=fct_reorder(type,month_current)) %>% 
  ggplot(aes(type,month_current,fill=material_type))+geom_col()+coord_flip()

#Material Used
brewing_materials %>%
  filter(!str_detect(material_type,"Total")) %>% 
  mutate(type=fct_reorder(type,month_current,sum)) %>% 
  ggplot(aes(date,month_current,fill=type))+geom_col()+
  scale_y_continuous(labels=scales::comma) +theme_bw()
  labs(x="Time",y="Pounds used in beer production",fill="Material Used")

#Grain or No Grain
brewing_materials %>%
  filter(str_detect(material_type,"Total.*products")) %>% 
  mutate(type=fct_reorder(type,month_current, sum)) %>% 
  ggplot(aes(date,month_current,fill=type))+geom_col()+
  scale_y_continuous(labels=scales::comma) + theme_bw()
  labs(x="Time",y="Pounds used in beer production",fill="Material Used")






```

BREWER SIZE AND NUMBER OF BREWERIES

```{r}
brewer_size <- brewer_size %>% 
  filter(brewer_size !="Total",!is.na(total_barrels)) %>% 
  mutate(avg_barrels = total_barrels/n_of_brewers) %>%
  mutate(brewer_size = fct_reorder(brewer_size,avg_barrels))
brewer_size %>%
  ggplot(aes(x = brewer_size, y = total_barrels)) + geom_jitter() + coord_flip()

brewer_size %>% 
  ggplot(aes(year,total_barrels,fill=brewer_size))+geom_col() + scale_fill_viridis_d()

brewer_size <- brewer_size %>%
  separate(brewer_size, into = c("lower", "upper"), sep = " to", remove = F) %>%
  mutate(upper = ifelse(lower == "Under 1 Barrel", 1, upper),
         upper = ifelse(lower == "Zero Barrels", 0, upper),
         lower = str_remove_all(lower, "[^\\d]"),
         upper = str_remove(upper, " Barrels")) %>%
  mutate(across(lower:upper, parse_number)) %>%
  mutate(upper = ifelse(brewer_size == "6,000,001 Barrels and Over", Inf, upper),
         lower = ifelse(brewer_size %in% c("Zero Barrels", "Under 1 Barrel"), 0, lower))

brewer_size %>%
  ggplot(aes(year, n_of_brewers, fill = factor(brewer_size))) +
  geom_col() +
  #scale_fill_continuous(trans = "log10") + 
  scale_x_continuous(breaks = 2009:2020)
```

NUMBER OF BARRELS CONSUMED ON PREMISES VS THOSE THAT END UP IN BOTTLES/CANS

```{r}

```
